Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural Morphemes

### 2019-01-25 Paper/AgreementAttraction.Rmd
firstdraft of a firstdraft

In this paper, our objective is to explore the source of agreement attraction effects in Turkish found by @Lago. The interpretation of their finding is complicated by the fact that in their possessive form all head nouns in their stimuli are morphologically ambiguous between possessive and accusative. Due to the mismatch in the frequency of usage of accusative and genitive, which is used as a attractor in this experiment, as a controller, @Lago's findings could potentially be explained with occasional shallow processing. We have replicated @Lago's experiment with unambigious head nouns, and we have found the same agreement attraction effects. However, this may mean that participants may engage in even more shallow processing than we imagined. We postulate that participants solely check for the presence of a *-lAr* morpheme, while largely disregarding the remainder of the sentence. We utilize an experiment design in which we use a relative clause with or without plural agreement on the verb in place of the genitive possessor since both verbal and nominal plural morphemes are the same in Turkish. If participants did, in fact, adopt a superficial processing strategy, we would expect to find a number agreement attraction effect similar in magnitude to @Lago's. However, if number attraction is not an artifact of shallow processing strategies, we should expect to find no number attraction in this experiment.

@@

Attraction errors in production and comprehension of subject-verb agrrement, in which a verb does not agree with the grammatical agreement controller, but with a potential attractors, have been the focal point of many research for quite a long time. In fact, it is still a widely researched are in psycholinguistic studies. Despite the thorough research that has been carried out, studies that have been conducted on agreement attraction in Turkish have been extremely few. In fact, @Lago has been the only study to look into this phenomenon in Turkish. @Lago's study make use of genitive-possessive structures in the subject position, in which the possessive-marked noun is the head of the noun phrase which acts as the grammatical agreement controller, and the genitive noun serves as a potential attractor. In a speeded acceptability judgment study, they found a significant effect of number agreement attraction. However, the interpretation of their finding may be a result of a non-subjecthood cues originating from their use of morphologically ambiguous forms of possessive. In their possessive form all head nouns in their stimuli are ambigiuous between possessive and accusative.

In Turkish, accusative number agreement controllers are extremely rare, while genitive agreement controllers are very frequent. Thus, @Lago's finding could possibly be explained by occasional shallow processing. When all syntactic relations in the sentence were processed fully, the possessive noun should have been identified as the controller. Meanwhile the genitive noun may sometimes have been erroneously identified as the controller during shallow processing, because genitives are more likely to act as agreement controllers than accusatives. A second alternative explanation of @Lago's finding may be the fact that participants may engage in even more shallow processing than outlined above. Participants may have erroneously responded *Yes* on some trials due to (i) the presence of a plural morpheme on a noun (attractor or controller) and (ii) the presence of a plural agreement morpheme on the verb. We speculate that on such trials, participants would have simply tried to check for the presence of such morphemes, while largely disregarding the remainder of the sentence.

We first replicated @Lago's experiment with unambiuous head nouns. To this end, we have revised the items that were used previously, to avoid morphological ambiguity between possessive and accusative forms. The effect found by @Lago replicates with unambiguous nouns as discused in \S 2.

\S 3 discussses the alternative account that posits even more shallow processing as mentioned above and offers a pre-registered experiment using RC attractors with possible outcomes and their indications. Since both nominal and verbal plural morphemes in Turkish take on the same form (*-ler* or *-lar* depending on the phonological environment), we can test this possibility with an experiment, in which we use relative clause with or without plural agreement on the verb in the place of the genitive possessors. An agreement attraction effect similar in magnitude to @Lago's would mean that participants use aforementioned strategies.

\S 4 presents a discussion revolving around possible 
Lastly, \S 5 offers a brief conclusion and presents topics for future researches.

# REPLICATON OF @Lago

In their study, @Lago investigated the comprehension of subject-verb agreement in Turkish-German bilinguals and Turkish monolinguals. They used speeded acceptability judments for the effects of number attraction in Turkish. Their sentences makes us of genitive-possessive constructions in the subject position, where the genitive is the attractor and the possessive is the head noun. They have manipulated the grammaticality of the sentence by changing the plural morphology of the verb, and they also manipulated the plurality of the attractor noun. In grammatical conditions, subject and the verb both bears the singular morphology with no overt morpheme. Moreover, in the ungrammatical conditions the verb bears the overt *-lAr* morpheme whereas the subject is still singular as exemplified below.

@@

They have found a significant effect of number attraction in Turkish ranging between 11%--15% across monolinguals. As seen from the results of statistical analysis in \textsc{Table} (\ref{lagomodel}), acceptability judgments showed an immense effect of grammaticality, and there is also interaction between grammaticality and attractor number which indicates an number attraction effect.

@@

According to @Lago's stipulation, Turkish genitive case does not provide a strong cue against subjecthood since it is extremely common to see genitive marked subjects in Turkish embedded clauses, as in example (\ref{gensubj}). Unlike English, genitive case is compatible with the subjecthood in English. Thus, @Lago attributes the robust agreement attraction effects to the case information.

@@

However, our first hypothesis was the possibility of participants engaging in a shallow processing, which ends up in a situation where not only genitive case but also possessive case plays a significant role in delivering the case information. None of the experimental items in @Lago has a head noun which ends with a vowel; thus, all of the possessive markers are morphologically and phonologically ambiguous between the accusative case and the possessive. Unlike genitive case, the accusative case in Turkish is extremely rare to see on the head noun of the subject, which only occurs in the raising predicates as in example (\ref{dsm}).

@@

In order to test this hypothesis, we have replicated the @Lago study with modified items, where the possessive is not ambiguous with the accusative case. We have tried to be as faithful as possible to the original sentences while trying to make sentences as plauisable as possible at the same time. We keep the semantic relation between the head nound and the controller the same with   A set of sentences are exemplified below.

@@

As seen in the examples unlike @Lago's experimental items, all of our items bear the *-sI* possessive marker instead of the ambiguous *-I* one. As for the filler items, we could not used or adapt from the original experimentsince the fillers of the original study were not online. We have used two types filler sentences: a grammatical ones where the verb bears plural agreement (\ref{fillera}), and an ungrammatical one where verb does not bear plural agreement (\ref{fillerb}). We wanted to nullify a possible strategy by the participants where they associate the sentence-final morpheme directly with the acceptability, and disregard other elements in the sentences when answering questions.

@@

All of our data, experimental materials, our experiment design, and as well as our fillers can be found at the Center for Open Science Framework website (https://osf.io/).

@@

One hundred seven Turkish speakers with mean age of X were recruited from the Bogazici University in {\.I}stanbul. We did not collect participants' knowledge of other languages; however, we ensured that Turkish is their native language and they predominantly used in their daily lives. In the experiments, participants are asked to judge the experimental and filler sentences whether or not they sound acceptable in Turkish. All of the sentences were presented one word at a time in the center area of the screen for 500 ms per word unlike @Lago and @Wagers2009, in which researches used 300 ms visual presentation per word. Experiment was run on a web-based platform Ibex Farm, and all of the documentation can be found in our osf and github page.

Before the experiment, they have been instructed to give accurate and quick answers with their own intuition, and they were also notified about the time limit for answering. At the start of the experiment they were given 4 practice items with feedbacks.

@@

In \textsc{Figure} (\ref{fig:replication}), y-axis shows proportion of "acceptable" answers, and x-axis indicates whether or not the sentences in that group is grammatical. Moreover, linetypes indicates an attractor noun with overt plural morphology. As seen from the figure, `r round(100*dataAvClean[1,7])`% of the sentences with plural attractors and singular verb were accepted by the participants following the findings of @Lago. We also see a number attraction rate of `r round(100*(dataAvClean[1,7]-dataAvClean[3,7]))`% which was already shown in @Lago with close results.

@@

\begin{figure}[H]
  \begin{floatrow}
    \ffigbox{%
```{r, fig.align = "right", echo = F}
print{}
```
    }{\caption{A figure}}

    \btabbox{%
```{r, fig.align = "right", echo = F}
knitr::kable(head(mtcars[,1:3]), format = "latex")
```
    }{\caption{A table}}
  \end{floatrow}
\end{figure}

# EXPERIMENT 2: RC ATTRACTOR
## Motivation
## Items and Fillers
## Expectations
## Possible Outcomes and Discussion

@@

Intro and repeat.

# ACKNOWLEDGEMENTS
We used the statistical language `R` `r citep(citation())` for all our analyses. These were implemented in dynamic rmarkdown documents using `knitr` `r citep(citation("knitr"))` and `rmarkdown` `r citep(citation("rmarkdown"))` packages. All graphs have been done with `ggplot` `r citep(citation("ggplot2"))`. Thank the Mine and Kadir for their student from courses.

@@

\newpage

```{r Table1, results='asis', echo=FALSE, cache=FALSE}
kable(head(iris), caption = "A glimpse of the famous *Iris* dataset.")
```

\newpage

```{r Table2, results='asis', echo=FALSE, cache=FALSE}
kable(mtcars[10:16, ], caption = "Now a subset of mtcars dataset.")
```

@@

\newpage

```{r Fig1, echo=FALSE, fig.cap="Just my first figure with a very fantastic caption.", cache=FALSE}
x <- rnorm(100)
y <- jitter(x, 1000)
plot(x, y)
```

\newpage

\blandscape

```{r Fig2, echo=FALSE, fig.cap="Second figure in landscape format.", cache=FALSE}
a <- sort(rnorm(100))
b <- c(rep("Group Small", 35), rep("Group Big", 65))
boxplot(a ~ b)
```

\elandscape

>>>>

In this paper, our objective is to explore the source of agreement attraction effects in Turkish discovered by @Lago. The interpretation of their finding is complicated by the fact that the possessive form of all head nouns used in their stimuli are morphologically ambiguous between possessive and accusative. In Turkish, genitive can be productively used for marking the subject of an embedded clause whereas accusative is rarely used for marking the subject. Due to this mismatch in the frequency of usage of accusative and genitive, which is used as a attractor in this experiment, as a controller, @Lago's findings could potentially be explained with occasional shallow processing. We have replicated @Lago's experiment with unambigious head nouns, and we have found similar agreement attraction effects. However, this may mean that participants engage in even more shallow processing than we imagined. We postulate that participants solely check for the presence of a *-lAr* morpheme, while largely disregarding the remainder of the sentence. We utilize an experiment design in which we use a relative clause with or without plural agreement on the verb in place of the genitive possessor since both verbal and nominal plural morphemes are the same in Turkish, i.e. the exponent of both is *-lAr*. If participants did, in fact, adopt a superficial processing strategy, we would expect to find a number agreement attraction effect similar in magnitude to that in @Lago. However, if number attraction is not an artifact of shallow processing strategies, we should expect to find no number attraction effects in this experiment.

@@

Attraction errors in the production and comprehension of subject-verb agreement, in which a verb does not agree with the grammatical agreement controller, but with a potential attractor, have been the main topic of research in many studies for quite a long time. In fact, it is still a widely researched area in psycholinguistic studies. Despite the comprehensive research that has been carried out, studies that have been conducted on agreement attraction in Turkish have been very limited. In fact, @Lago is currently the only study that explores this phenomenon in Turkish. @Lago  makes use of genitive-possessive structures in the subject position, in which the possessive-marked noun is the head of the noun phrase which acts as the grammatical agreement controller, and the genitive noun serves as a potential attractor. In a speeded acceptability judgment study, @Lago found a significant effect of number agreement attraction. However, the interpretation of their findings may be a result of the fact that non-subjecthood cues originate from their use of morphologically ambiguous forms of the possessive. In the possessive forms that are used, all the head nouns in their stimuli are ambigiuous between possessive and accusative.

In Turkish, accusative number agreement controllers are extremely rare, while genitive agreement controllers are very frequent. Thus, @Lago's finding could potentially be explained with occasional shallow processing. When all syntactic relations in the sentence were processed fully, the possessive noun may have been identified as the controller. Meanwhile, the genitive noun may sometimes have been erroneously identified as the controller during shallow processing because genitives are more likely to act as agreement controllers than accusatives (SOURCE). A second alternative explanation for @Lago's findings may be the fact that participants may engage in even more shallow processing than outlined above. Participants may have erroneously responded *Yes* on some trials for two main reasons: (i) the presence of a plural morpheme on a noun (attractor or controller), and (ii) the presence of a plural agreement morpheme on the verb. We speculate that in such trials, participants would have simply tried to check for the presence of such morphemes, while largely disregarding the remainder of the sentence.

We first replicated @Lago's experiment with unambiguous head nouns. To this end, we revised the items that were used previously in order to avoid morphological ambiguity between possessive and accusative forms. The effect found in @Lago was also observed when unambiguous nouns were used, as will be discussed in \S 2.

\S 3 discusses the alternative account that posits even more shallow processing as mentioned above and presents a pre-registered experiment using RC attractors with potential outcomes and their indications. Since both nominal and verbal plural morphemes in Turkish are expressed with the same form (*-ler* or *-lar* depending on the phonological environment), we can test this possibility with an experiment in which a relative clause with or without plural agreement on the verb in place of the genitive possessors is used. An agreement attraction effect similar in magnitude to that observed in @Lago would indicate that participants use the aforementioned strategies.

\S 4 offers a discussion of the issue of number attraction and where this experiments leaves us. Lastly, \S 5 presents a brief conclusion and topics for future research.

# REPLICATON OF LAGO ET AL. (2018)

In their study, @Lago investigate the comprehension of subject-verb agreement in Turkish-German bilinguals and Turkish monolinguals. They use speeded acceptability judgments for the effects of number attraction in Turkish. Their sentences make us of genitive-possessive constructions in the subject position, where the genitive is the attractor and the possessive is the head noun. They manipulate the grammaticality of the sentence by changing the plural morphology of the verb, and they also manipulate the plurality of the attractor noun. In grammatical conditions, the subject and the verb both bear singular morphology with no overt morpheme. Moreover, in the ungrammatical conditions, the verb bears the overt *-lAr* morpheme whereas the subject is still singular as exemplified below.

@@

They found a significant effect of number attraction in Turkish ranging between 11\%--15\% across monolinguals. As seen in the results of the statistical analysis in \textsc{Table} (\ref{lagomodel}), the acceptability judgments showed an immense effect of grammaticality, and there is also interaction between grammaticality and attractor number, which indicates the presence of a number attraction effect.

@@

@Lago stipulate that the Turkish genitive case does not provide a strong cue against subjecthood since Turkish frequently makes use of genitive marked subjects in embedded clauses, as in example (\ref{gensubj}). This is in contrast with English, in which the genitive case is compatible with subjecthood. Thus, @Lago argue that this robust agreement attraction effect has been linked to the case information carried by accusative and genitive.

@@

However, our initial hypothesis postulates that participants engage in shallow processing, which results in a situation in which not only the genitive case but also the possessive case plays a significant role in delivering the case information. None of the experimental items in @Lago have a head noun which ends with a vowel; thus, all of the possessive markers are morphologically and phonologically ambiguous between the accusative case and the possessive. Unlike genitive case, it is extremely rare for the accusative case to appear on the head noun of the subject, which only occurs in raising predicates as in example (\ref{dsm}).

@@

In order to test this hypothesis, we have replicated the experiment of @Lago with modified items, in which the possessive is not ambiguous with the accusative case. We tried to be as faithful as possible to the original sentences while also trying to make the sentences as plausable as possible. We keep the semantic relation between the head noun and the controller the same with what has been described in @Lago's study, which is either a relation regarding profession or a service that is given by the head noun for the possessor. A set of sentences are exemplified below.

@@

As seen in the examples, unlike @Lago's experimental items, all of our items bear the *-sI* possessive marker instead of the ambiguous *-I* marker. As for the filler items, we could not use or modify the original experiment items since the fillers of the original study were not online. We have used two types filler sentences: grammatical sentences in which the verb bears plural agreement (\ref{fillera}), and ungrammatical sentences in which the verb does not bear plural agreement (\ref{fillerb}). We wanted to nullify a possible strategy by the participants where they associate the sentence-final morpheme directly with the acceptability of the sentence. And we also wanted to eliminate the possibility of participants disregarding other elements in the sentences while answering the questions we ask right after the sentence.

@@

All of our data, experimental materials, our experiment design, and our fillers can be found on the website of the Center for Open Science Framework (https://osf.io/).

@@

One hundred and seven Turkish speakers with a mean age of X were recruited from Bogazici University in İstanbul. We did not collect participants' knowledge of other languages; however, we verified that Turkish is their native language and that they predominantly use it in their daily lives. In the experiments, participants were asked to judge the acceptability of experimental and filler sentences in Turkish. All of the sentences were presented one word at a time in the center of the screen for 500 ms per word unlike @Lago and @Wagers2009, in which the duration was 300 ms per word. The experiment was run on a web-based platform titled the Ibex Farm, and all of the documentation can be found on our osf and github page.

Before the experiment, participants were instructed to give accurate and quick answers based on their own intuitions, and they were also notified about the time limit for answering. At the start of the experiment, they were given 4 practice items with feedback.

@@

In \textsc{Figure} (1), the y-axis shows the percentage of "acceptable" answers, and the x-axis indicates whether or not the sentences in that group are grammatical. Moreover, the linet ypes indicate an attractor noun with overt plural morphology. As seen in the figure, `r round(100*dataAvClean[1,7])`% of the sentences with plural attractors and a singular verb were accepted by the participants, in line with the findings of @Lago. We also see a number attraction rate of `r round(100*(dataAvClean[1,7]-dataAvClean[3,7]))`% which was also observed in @Lago with close results.

@@

And yes, I plan to beautify the figures.
\begin{figure}[H]
  \begin{floatrow}
    \ffigbox{%
```{r, fig.width = 4 , fig.height = 4 , fig.align = "right", echo = F}
print(plot_average)
```
    }{\caption{A figure}}

    \btabbox{%
```{r, fig.align = "right", echo = F}

```
    }{\caption{A table}}
  \end{floatrow}
\end{figure}

# EXPERIMENT 2: RC ATTRACTOR

Even though our first hypothesis regarding shallow processing did not hold, we still need to entertain the second possibility we have discussed in this paper. Participants may indeed engage in an even shallower process of sentence comprehension, in which they merely match the use of *-lAr*. Moreover, we still need to discuss how much it is an effect of case information rather than only a number attraction. We have seen that the anti-subjecthood cues of the accusative are not significant since in both cases where the possessive is ambiguous with the accusative and the possessive is clearly marked, we have observed extremely close results in the speeded acceptability judgments.

In order to check both the sole effect of number agreement and the possibility of a task effect, we propose an experiment design in which a head noun is a bare NP, is not marked with any other morpheme and preceded by a relative clause construction. This relative clause consists of only a verbal component, which bears an overt plural marker. Since Turkish verbal and nominal plural morphemes are identical, we plan to check the participants' strategy with regards to whether or not it is a cue that helps in the reconstruction of the ungrammatical sentence or whether it is merely a task effect in which participants disregard the rest of the sentence and focus the existence of the morpheme *-lAr*.

## Materials

Like genitive-possessive structures, attractors do not intervene between the grammatical agreement controller and the verb in relative clause constructions. Turkish relative clauses always precede the head noun, except for in special cases in which they are marked with unique prosody. Item (\ref{rcexample}) is an example of a RC structure, and item (\ref{rcexample2}) shows the possibility of using only the verbal component of the relative clause since it is grammatical to drop arguments in Turkish. ( add a footnote here giving the details of such events, and restrictions. )

\begin{exe}
\ex
\begin{xlist}
\ex \label{rcexample}
\gll On-lar-{\i}n ev-e gel-me-den g\"{o}r-d\"{u}k-ler-i \c{c}ocuk so\u{g}uk-ta \"{u}\c{s}\"{u}-m\"{u}\c{s}-t\"{u}.\\
they-\textsc{pl}-\textsc{gen} home-\textsc{dat} come-\textsc{neg}-\textsc{abl} see-\textsc{nlmz}-\textsc{pl}-\textsc{poss} kid cold--\textsc{loc} feel.chilly-\textsc{perf}-\textsc{pst}\\
\glt The kid that they saw right before coming to home was feeling chilly. 
\ex \label{rcexample2}
\gll G\"{o}r-d\"{u}k-ler-i \c{c}ocuk so\u{g}uk-ta \"{u}\c{s}\"{u}-m\"{u}\c{s}-t\"{u}.\\
see-\textsc{nlmz}-\textsc{pl}-\textsc{poss} kid cold--\textsc{loc} feel.chilly-\textsc{perf}-\textsc{pst}\\
\glt The kid that they saw home was feeling chilly.
\end{xlist}
\end{exe}

As for the experimental sentences, we plan to use sentences that are similar to the ones used in @Lago. Instead of a genitive controller, we utilize an RC, which we manipulate for its values for bearing the plural morpheme. The head noun of the subject is always singular, and it is followed by a 2/3 word adverbial. Moreover, the matrix verb of the sentences is also manipulated in terms of plurality, deeming the sentence grammatical or ungrammatical. Lastly, the relative clause has to be an object relative clause, since Turkish subject relative clauses never bear a plural morpheme on the embedded verb. As in the @Lago's study and our replication, we will have a four condition, where we manipulate the plurality of the attractor (*plural/singular*) and the grammaticality of the sentece by using overt plural morphology (*grammatical/ungrammatical*), which are demonstrated with item (\ref{reg1}), (\ref{reg2}), (\ref{reg3}), and (\ref{reg4})

\begin{exe}
\ex
\begin{xlist}
\ex \underline{Grammatical, SG attractor} \label{reg1}
\gll D\"{o}v-d\"{u}\u{g}-\"{u} \c{c}ocuk mutfak-ta bayg{\i}n hal-de yat-{\i}yor-du.\\
beat-\textsc{nmlz}-\textsc{poss} kid kitchen-\textsc{loc} unconscious state-\textsc{loc} lie-\textsc{prog}-\textsc{pst}\\ 
\glt The kid that he/she beats was laying in the kitchen unconscious.
\ex \underline{Grammatical, PL attractor} \label{reg2}
\gll D\"{o}v-d\"{u}k-ler-i \c{c}ocuk mutfak-ta bayg{\i}n hal-de yat-{\i}yor-du.\\
beat-\textsc{nmlz}-\textsc{pl}-\textsc{poss} kid kitchen-\textsc{loc} unconscious state-\textsc{loc} lie-\textsc{prog}-\textsc{pst}\\
\glt The kid that they beat was laying in the kitchen unconscious.
\ex \underline{Ungrammatical, PL attractor} \label{reg3}
\gll D\"{o}v-d\"{u}k-ler-i \c{c}ocuk mutfak-ta bayg{\i}n hal-de yat-{\i}yor-lar-d{\i}.\\
beat-\textsc{nmlz}-\textsc{pl}-\textsc{poss} kid kitchen-\textsc{loc} unconscious state-\textsc{loc} lie-\textsc{prog}-\textsc{pl}-\textsc{pst}\\
\glt Intended: The kid that they beat were laying in the kitchen unconscious.
\ex \underline{Ungrammatical, SG attractor} \label{reg4}
\gll D\"{o}v-d\"{u}\u{g}-\"{u} \c{c}ocuk mutfak-ta bayg{\i}n hal-de yat-{\i}yor-lar-d{\i}.\\
beat-\textsc{nmlz}-\textsc{poss} kid kitchen-\textsc{loc} unconscious state-\textsc{loc} lie-\textsc{prog}-\textsc{pl}-\textsc{pst}\\
\glt Intended: The kid that he/she beats were laying in the kitchen unconscious.
\end{xlist}
\end{exe}

As for the fillers, we need two different set of fillers in order to counterbalance the ever-present grammaticality of singular and plural verbs. For grammatical fillers with a plural verb (example (\ref{fillerreg1})) we propose a structure in which the head noun is followed by a converb. With this modification, the controller of the experimental sentences becomes a controller for a subclause, and the main verb is saturated with another subject introduced right after the subclause.

For ungrammatical fillers with a singular verb (example (\ref{fillerreg2})), we have used strictly transitive verbs without an overt object. By utilizing the same structure with the other type of fillers, we ensure that participants will not come up with a strategy in which they always check the second word for dependency resolution. The controller of the fillers and the controller of the experimental items differ in the linear order they are shown in the experiment.

Question: Can we do subject relative clause here? Like durdurulan ogrenci.

\begin{exe}
\ex
\begin{xlist}
\ex \label{fillerreg1}
\gll Dur-dur-duk-lar-{\i} \"{o}\u{g}renci \c{s}a\c{s}{\i}r-{\i}nca arkada\c{s}-lar-{\i} birden g\"{u}l-d\"{u}-ler.\\
stop-\textsc{caus}-\textsc{nmlz}-\textsc{pl}-\textsc{poss} student surprise-\textsc{cvb} friend-\textsc{pl}-\textsc{poss} suddenly laugh--\textsc{pst}-\textsc{pl}\\
\glt When the student which was stopped surprised, his friends burst out laughing.
\ex \label{fillerreg2}
\gll *Tut-tuk-lar-{\i} a\c{s}\c{c}{\i} gel-me-yince dan{\i}\c{s}man-lar hala ver-di.\\
hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss} cook come--\textsc{neg}-\textsc{cvb} advisor-\textsc{pl} still give-\textsc{pst}\\
\glt Inteded: When the cook that they hired did not come, advisors did not still give. 
\end{xlist}
\end{exe}

We plan to have participants from the undergrad students of Bogazici University, which will be given an extra credit incentive. They will again carry out the experiment on an online experiment platform Ibex Farm. The experiment process will be exactly the same with the replication of @Lago, including descriptions before the experiment, the layout of the experiment, the time spared for visualization of every word, exclusion criteria, and analysis.

## Expectations

(This part is extremely tentative)

Our objective is to explore the number attraction phenomenon without the effects of case information and without the limits of nominal paradigm. By doing so, we expect participants to engage with the sentences which are ungrammatical in an extremely shallow fashion. We argue that instead of reconstructing the sentence utilizing every detail from the attractor and the controller, participants disregard the information from other sources in the sentence and look for a matching morpheme, i.e. *-lAr*.

In the case that there will be a similar attraction effects with the replication of @Lago and @Lago study, we think that... what do we think? I need to talk about the paper and idea more thoroughly, I guess. Because I feel like I am repeating myself.

@@

In this paper, we have entertained the idea of task effect in the so-called Turkish number attraction phenomenon. We argue that the findings of the @Lago study is not clear and there are too many variables to account for in the experiment, one of them being the ambiguous morphology that the head noun bears. In the first experiment, we have replicated the attraction task of @Lago. We have found the similar effects of agreement with a bigger pool of participants. Then, for entertaining the other possibility in which we argue that participants do not fully reconstruct the sentence; however, they make us of the direct cue of overt morpheme *-lAr*, we offer an experiment where we use object relative clauses as an attractor.

# ACKNOWLEDGEMENTS
We used the statistical language `R` `r citep(citation())` for all our analyses. These were implemented in dynamic rmarkdown documents using `knitr` `r citep(citation("knitr"))` and `rmarkdown` `r citep(citation("rmarkdown"))` packages. All graphs have been done with `ggplot` `r citep(citation("ggplot2"))`. We also would like to thank Mine Nakipo\u{g}lu and Kadir Gökgöz for giving us the oppurtunity to conduct experiments and having participants from their classes.

@@

@@
